\clearpage
\setcounter{page}{1}
\begin{center}
{\bf \huge Robbery 101 - Prerequisite Quiz}
\end{center}
\vskip -5pt

\noindent\makebox[\linewidth]{\rule{\paperwidth}{0.6pt}}
\vskip 7pt
{\bf \Large Name (in print):} \hskip 5cm {\bf \Large Lab Instructor: } 
\vskip 5pt
\noindent\makebox[\linewidth]{\rule{\paperwidth}{0.6pt}}
\vskip 5pt
\noindent  You must earn a score of 5 or 6 to pass; questions are graded as either {\bf correct} or {\bf incorrect} with no partial credit.
\vskip 5pt
\noindent\makebox[\linewidth]{\rule{\paperwidth}{0.6pt}}
\vskip 5pt


\begin{multicols}{2}
\begin{enumerate}\setcounter{enumi}{0}
%Question Pool 1 for Learning Goal 1
    \item 
    \ifthenelse{\one=1}{
     What color is get away car?
    \ifthenelse{\boolean{show}}{\begin{sol}Green \end{sol}}{}
    }{
     \ifthenelse{\one=2}{
     What is make of the get away car?
    \ifthenelse{\boolean{show}}{\begin{sol} Chevy   \end{sol}}{}
    }{
    \ifthenelse{ \one=3}{
    What is the model of the get away car?
    \ifthenelse{\boolean{show}}{\begin{sol} 1966    \end{sol}}{}
    }{
    \ifthenelse{ \one=4}{
   How many tires does the get away car have?
    \ifthenelse{\boolean{show}}{\begin{sol} 3   \end{sol}}{}
    }{
    \ifthenelse{\one=5}{
    How many door handles does the get away car have?
   \ifthenelse{\boolean{show}}{\begin{sol}  3  \end{sol}}{}
    }{
    \ifthenelse {\one=0}{
    How many side mirror does the get away care have?
    \ifthenelse{\boolean{show}}{\begin{sol} None   \end{sol}}{}
    }{
    }}}}}}


\vskip 2cm
%Question Pool 2 for Learning Goal 2
    \item 
    \ifthenelse{\two=1}{
    What is the bank's address?
    \ifthenelse{\boolean{show}}{\begin{sol}666 Side street \end{sol}}{}
    }{
     \ifthenelse {\two=2}{
   How many entrance does the bank have?
   \ifthenelse{\boolean{show}}{ \begin{sol}   3 \end{sol}}{}
    }{
    \ifthenelse  {\two=3}{
    What is the bank phone number?
    \ifthenelse{\boolean{show}}{\begin{sol}555-6666    \end{sol}}{}
    }{
    \ifthenelse  {\two=4}{
    Which of security camera's have a blind spot?
    \ifthenelse{\boolean{show}}{\begin{sol}The one on the left-side street    \end{sol}}{}
    }{
    \ifthenelse {\two=5}{
    How many tellers work at the bank?
    \ifthenelse{\boolean{show}}{\begin{sol} 5   \end{sol}}{}
    }{
    \ifthenelse {\two=0}{
    Where is the bank's vault? 
    \ifthenelse{\boolean{show}}{\begin{sol}  In the back  \end{sol}}{}
    }{
   }}}}}}


\vskip 2cm

%Question Pool 3 for Learning Goal 3
    \item 
    \ifthenelse{  \three=1}{
    How many guards are there?
    \ifthenelse{\boolean{show}}{\begin{sol}   5 \end{sol}}{}
    }{
     \ifthenelse  {\three=2}{
     Which guard is most distracted?
   \ifthenelse{\boolean{show}}{ \begin{sol} The gamer.   \end{sol}}{}
    }{
    \ifthenelse {\three=3}{
     What kind of weapons do guards carry? 
   \ifthenelse{\boolean{show}}{ \begin{sol}  Taser and pepper spray.  \end{sol}}{}
    }{
    \ifthenelse {\three=4}{
    What are we going to do with the guards? 
   \ifthenelse{\boolean{show}}{\begin{sol} Tickle them to the ground.   \end{sol}}{}
    }{
    \ifthenelse {\three=5}{
     Where in the bank is the most detracted guard sitting?
    \ifthenelse{\boolean{show}}{\begin{sol}   Next to the teller on my left. \end{sol}}{}
    }{
    \ifthenelse {\three=0}{
    Which guard is most ticklish?
    \ifthenelse{\boolean{show}}{\begin{sol} The guard on the Side street entrance.   \end{sol}}{}
    }{
   }}}}}}
\end{enumerate}


\vskip 2.5cm

\columnbreak
\begin{enumerate}\setcounter{enumi}{3} 
%Question Pool 4 for Learning Goal 4
\item 
    \ifthenelse {\four=1}{
    What time we meet at Mr. Pink's house?
  \ifthenelse{\boolean{show}}{  \begin{sol}  Tuesday 10am.  \end{sol}}{}
    }{
     \ifthenelse {\four=2}{
    What time do we head to the bank from Mr. Pink's house?
   \ifthenelse{\boolean{show}}{ \begin{sol}  Tuesday 11:30 am  \end{sol}}{}
    }{
    \ifthenelse {\four=3}{
    What time are we entering the bank?
   \ifthenelse{\boolean{show}}{ \begin{sol}  Tuesday 12:30 pm.  \end{sol}}{}
    }{
    \ifthenelse  {\four=4}{
     What time does the getaway car go vroom vroom out of Side Street?
   \ifthenelse{\boolean{show}}{  \begin{sol} Tuesday 12:45 pm. You better be in it before that or you are on your own.   \end{sol}}{}
    }{
    \ifthenelse {\four=5}{
    What time and where do we split the money?
   \ifthenelse{\boolean{show}}{ \begin{sol}  Tuesday at 2 pm sharp at Ms. Green's office.  \end{sol}}{}
    }{
    \ifthenelse  {\four=0}{
     When is the meeting after we split the money?
   \ifthenelse{\boolean{show}}{ \begin{sol} Never! this is a trick question!   \end{sol}}{}
    }{
}}}}}}


\vskip 2cm

%Question Pool 5 for Learning Goal 5
    \item 
    \ifthenelse  {\five=1}{
 What color cloths are recommended for the main event?
  \ifthenelse{\boolean{show}}{  \begin{sol}Black\end{sol}}{}
    }{
     \ifthenelse {\five=2}{
     Are we allowed to wear costumes for the main event 
   \ifthenelse{\boolean{show}}{ \begin{sol}Yes! As long as it you wear a mask.     \end{sol}}{}
    }{
    \ifthenelse {\five=3}{
   What do we wear over our heads for the main event?
   \ifthenelse{\boolean{show}}{ \begin{sol} Stockings.    \end{sol}}{}
    }{
    \ifthenelse {\five=4}{
    What kind of shoes do we wear for the main event? 
   \ifthenelse{\boolean{show}}{\begin{sol}  Tennis shoes.  \end{sol}}{}
    }{
    \ifthenelse {\five=5}{
    What kind of hand bag do we carry during  the main event

   \ifthenelse{\boolean{show}}{\begin{sol} Large ones.   \end{sol}}{}
    }{
    \ifthenelse {\five=0}{
    Can we take off our stockings to breathe during  the main event?

   \ifthenelse{\boolean{show}}{ \begin{sol}  No!  \end{sol}}{}
    }{
   }}}}}}
\vskip 2cm

%----------------------------------------------------------------------------
%----------------------------------------------------------------------------
%----------------------------------------------------------------------------
%\pagebreak
%----------------------------------------------------------------------------

%Question Pool 6 for Learning Goal 6
    \item 
    \ifthenelse {\six=1}{
   Can I tell my mom what I am doing on Tuesday?
   \ifthenelse{\boolean{show}}{ \begin{sol}NO!\end{sol}}{}
    }{
     \ifthenelse {\six=2}{
    Can I tell my neighbour that I am disappearing from the neighbourhood after Tuesday?  
   \ifthenelse{\boolean{show}}{ \begin{sol}  NO!  \end{sol}}{}
    }{
    \ifthenelse {\six=3}{
    Can I spend all my money on Wednesday?
    \ifthenelse{\boolean{show}}{\begin{sol}  NO!  \end{sol}}{}
    }{
    \ifthenelse  {\six=4}{
    Can I write a memoir about the robbery and sell it for  twice as much money?
   \ifthenelse{\boolean{show}}{\begin{sol} NO!   \end{sol}}{}
    }{
    \ifthenelse {\six=5}{
     Can I do an interview with our local channel about the adventures of my Bank robbery? 
   \ifthenelse{\boolean{show}}{\begin{sol} NO!   \end{sol}}{}
    }{
    \ifthenelse {\six=0}{
    Can I tell the tale of the robbery to my cell mate? 
   \ifthenelse{\boolean{show}}{ \begin{sol}  Are we all in jail for the robbery, then that is ok! Otherwise, NO!  \end{sol}}{}
    }{
    }}}}}}
\end{enumerate}

\vskip 3.5cm

\end{multicols}
    
    

\pagebreak
